Integration of Multimedia Collections and Tools for Interaction with Digital Content. The case study of the Archaia Kypriaki Grammateia Digital Corpus

### 2016-02-10 source/10/Paper proposal for EAGLE final.tex
further changes to verge, Graham and fixes to Vassallo

The third text version of this text is mentioned in the commentary and based on the information provided (two similar
texts and a reference to a ``copy'') one would expect that it was very similar. The same editorial practice is employed
in the parallel column dedications from a different benefactor (I.Aph 7 \& I.Aph 8), where 2nd version of the text is
noted (IAph 1.8) but only one (I.Aph 1.7, MAMA 450) was published. The apparent verisimilitude of the column
dedications is corroborated by the published images, which depict two inscriptions (MAMA 437 and MAMA 450) with similar
late 1st c. BC/early 1st c. AD lettering. When publishing a large corpus of inscriptions, referring to copies is
understandable. However, treating texts as ``copies'' as opposed to individual monuments can, and in this case will,
prove problematic.\footnote{ For another study of ``copy'' inscriptions at Aphrodisias see Graham 2015 (forthcoming).}
While MAMA VIII offered a broader audience access to the inscriptions at Aphrodisias, the approach to the inscriptions
and the quality of the images also imposed limitations that made it difficult to analyse the physical elements of the
inscription or to question the proposed texts and restorations.

@@

The benefits and the challenges observed in the IAph 2007 digital publication are applicable to a number of digital
resources. As we attempt to bring corpora of unprecedented size to a digital realm, we must consider not only how we
represent this information but how we engage a wider readership in epigraphic materials. It would not take a great deal
of work to augment the scope of IAph 2007 from an academic resource into one also achieves a didactic aim of
illustrating how we use different elements of an inscription (including letter forms) to suggest a date for an inscription. The point is not necessarily to establish a firm date, but to provide greater transparency to process by which we formulate dates. We have the potential now, to present inscriptions at
face value, not only as texts but as contradictory objects whose stories, whether conveyed on stone or a computer app,
are subject to the same conventions, complexities and imperfections as the humans who created them.

>>>>

The third text version of this text is mentioned in the commentary and based on the information provided (two similar
texts and a reference to a ``copy'') one would expect that it was very similar. The same editorial practice is employed
in the parallel column dedications from a different benefactor (I.Aph 7 \& I.Aph 8), where 2nd version of the text is
noted (IAph 1.8) but only one (I.Aph 1.7, MAMA 450) was published. The apparent verisimilitude of the column
dedications is corroborated by the published images, which depict two inscriptions (MAMA 437 and MAMA 450) with similar
late 1st c. BC/early 1st c. AD lettering. When publishing a large corpus of inscriptions, referring to copies is
understandable. However, treating texts as ``copies'' as opposed to individual monuments can, and in this case will,
prove problematic.\footnote{ For another study of ``copy'' inscriptions at Aphrodisias  \citet{Graham2015}.}
While MAMA VIII offered a broader audience access to the inscriptions at Aphrodisias, the approach to the inscriptions
and the quality of the images also imposed limitations that made it difficult to analyse the physical elements of the
inscription or to question the proposed texts and restorations.

@@

The benefits and the challenges observed in the IAph 2007 digital publication are applicable to a number of digital
resources. As we attempt to bring corpora of unprecedented size to a digital realm, we must consider not only how we
represent this information but how we engage a wider readership in epigraphic materials. It would not take a great deal
of work to augment the scope of IAph 2007 from an academic resource into one that also achieves a didactic aim of
illustrating how we use different elements of an inscription (including letter forms) to suggest a date for an inscription. The point is not necessarily to establish a firm date, but to provide greater transparency to process by which we formulate dates. We have the potential now, to present inscriptions at
face value, not only as texts but as contradictory objects whose stories, whether conveyed on stone or a computer app,
are subject to the same conventions, complexities and imperfections as the humans who created them.

### 2016-02-10 source/44/Damnjanovic_et_al_EAGLE2016.tex
further changes to verge, Graham and fixes to Vassallo

%%%%%%%%
%TITLE:%
%%%%%%%%
\title{Integration of Multimedia Collections and Tools
for Interaction with Digital Content.
The case study of the Archaia Kypriaki Grammateia Digital Corpus}
\author[cyi]{Valentina Vassallo\corref{first}}
\author[cyi]{Uros Damnjanovic}
\author[cyi]{Sorin Hermon}
\date{2015-11-26}
\cortext[first]{Corresponding author. Email: (u.damnjanovic, v.vassallo, s.hermon@cyi.ac.cy}
\begin{document}

@@

The metadata schema is organized in groups corresponding to different research areas clustered in wrappers and
sub-wrappers, in order to fully describe all information that the ‘asset inscription’ contains. This schema,
distinguished by its multidisciplinary structure, include all disciplines relevant for description and representation
of epigraphies: archaeology (investigating for example the context of the finds), philology s(analyzing the text, the
writing style, the scripture), chemistry and geology (providing details on the material upon which inscriptions were
carved), conservation (giving information about the state of the artefact), visualization and museology (about the
museums and places of conservation).

@@

\begin{itemize}
\item the creation and use of relations that are able to aggregate all the resources under a specific resource
identified as reference item.
\item the creation of rules for the development of a script that will be able to map to the Eagle data model every time
according to the type of object we are dealing with. This implies also an editing of the metadata, creating single
items that have as head the information about the inscription (e.g. the Ancient Greek text) and to which are attached
all the other metadata sets concerning the related objects (e.g. the Modern Greek text, the image support of the
inscription, the commentary, the 3D of the support-inscription, etc.).
\end{itemize}
Even if the first solution would be much faster from a technical point of view, at the moment is under preparation a
test for the second solution. In fact the latter, even if it is time-consuming in terms of elaboration, seems to be the
best solution for avoiding data duplication and for having more cohesive data.

@@

We presented in this paper a digital data repository and showed number of innovative tools used to access and explore
its collections. One of the most interesting collection stored in the repository is the Archaia Kypriaki Grammateia
Digital Corpus composed of Ancient Greek and Latin epigraphic texts. We argued that by interacting with data in an
innovative ways can help users better understand data and stimulate knowledge creation. With the set of proposed
functionalities we also enabled exploration of the epigraphic text in a way that supports sense making, understanding
and collaboration. We also showed how the collection of epigraphic texts can be used within other projects by mapping
our data to the appropriate data formats. Next step is to set up an evaluation framework that will try to measure and
evaluate the contribution of each tool to the users daily tasks. We want to measure the benefits of using such a tools
by performing various evaluation tasks and measuring the user's performance.

>>>>

%%%%%%%%
%TITLE:%
%%%%%%%%
\title{Integration of Multimedia Collections and Tools
for Interaction with Digital Content. The case study of the Archaia Kypriaki Grammateia Digital Corpus}
\author[cyi]{Uros Damnjanovic}
\author[cyi]{Valentina Vassallo\corref{first}}
\author[cyi]{Sorin Hermon}
\date{2015-11-26}
\cortext[first]{Corresponding author. Email: u.damnjanovic, v.vassallo, s.hermon@cyi.ac.cy}
\begin{document}

@@

The metadata schema is organized in groups corresponding to different research areas clustered in wrappers and
sub-wrappers, in order to fully describe all information that the ‘asset inscription’ contains. This schema,
distinguished by its multidisciplinary structure, include all disciplines relevant for description and representation
of epigraphies: archaeology (investigating for example the context of the finds), philology (analyzing the text, the
writing style, the scripture), chemistry and geology (providing details on the material upon which inscriptions were
carved), conservation (giving information about the state of the artefact), visualization and museology (about the
museums and places of conservation).

@@

\begin{itemize}
\item the creation and use of relations that are able to aggregate all the resources under a specific resource
identified as reference item.
\item the creation of rules for the development of a script that will be able to map to the EAGLE data model every time
according to the type of object we are dealing with. This implies also an editing of the metadata, creating single
items that have as head the information about the inscription (e.g. the Ancient Greek text) and to which are attached
all the other metadata sets concerning the related objects (e.g. the Modern Greek text, the image support of the
inscription, the commentary, the 3D of the support-inscription, etc.).
\end{itemize}
Even if the first solution would be much faster from a technical point of view, at the moment is under preparation a
test for the second solution. In fact the latter, even if it is time-consuming in terms of elaboration, seems to be the
best solution for avoiding data duplication and for having more cohesive data.

@@

We presented in this paper a digital data repository and showed number of innovative tools used to access and explore
its collections. We argued that by interacting with data in an
innovative ways can help users better understand data and stimulate knowledge creation. One of the most interesting collection stored in the repository is the Archaia Kypriaki Grammateia
Digital Corpus composed of Ancient Greek and Latin epigraphic texts. With the set of proposed
functionalities we also enabled exploration of the epigraphic text in a way that supports sense making, understanding
and collaboration. We also showed how the collection of epigraphic texts can be used within other projects by mapping
our data to the appropriate data formats. Next step is to set up an evaluation framework that will try to measure and
evaluate the contribution of each tool to the users daily tasks. We want to measure the benefits of using such a tools
by performing various evaluation tasks and measuring the user's performance.
